---
execute: 
  echo: false
  message: false
  warning: false
---

## Introduction

This project aims to explore the relationship between annual income and universities. This data was pulled from Kaggles. By analyzing a data set that includes annual income and information about various universities, I want to answer the question: 

***What is probability that someone makes more than 50k.***

The Model below shows the overall data in comparison to other Universities.

```{r}
library(tidyverse)
library(gganimate)
```

```{r}
#| output: false

x <- read_csv(file = "data/2013_Salaries__Pennsylvania_State_System_of_Higher_Education.csv", col_names = TRUE, show_col_types = FALSE)  
  
x <- rename(x, "uni" = "University or Office",  "pay" = "Base Pay")

x <- x |> 
  select(pay, uni) |> 
  drop_na() |> 
  filter(uni != "Office of the Chancellor")

x$pay <- parse_number(x$pay)
  
data.frame(x)

```

```{r}
x |> 
  ggplot(
    aes(x = uni, y = pay)
  )+
  geom_boxplot() +
  theme_classic()+
  scale_y_continuous(labels = scales::label_number_si())+
  theme(
    axis.text.x = element_text(angle = 300, hjust = 0),
    axis.title.y = element_text()
        )+
  labs(
    title = "Annual Income of Graduate from Universities in Pennsylvania",
    subtitle = "The Median income of all the Graduates is between 60k-70k",
    x = "University", y = "      Income (thousands)      "
  )
```

## Conclusion of the Model

##### Pay Amounts: 

- The pay amounts vary across the dataset, ranging from $1,245 to $275,000. There seem to be fluctuations in pay between different universities.

##### Range: 

- Over 90% of the graduates make less that 100k. Thats 11,200 observations in 12,400

- The remaining 10% make anywhere between 107,870 to 275,000
    
